Python as a machine learning language: experiences from the scikit-learn project

### 2013-06-12 paper.tex
remove some comments
wording

In a previous paper \citep{pedregosa2011}, \sklearn was briefly presented and
benchmarked against several competitors. In this paper, we instead focus on an
in-depth discussion and analysis of the design choices used in building the
library. First, in section \ref{sec:core-api}, we present the central application
programming interface (API) and then describe, in section \ref{sec:advanced-api},
advanced API mechanisms built on this core API. Section
\ref{sec:implementation} describes implementation trade-offs and analyzes
limitations of the technologies we rely on, while section
\ref{sec:comparison} then compares \emph{scikit-learn} to other major projects in
terms of API. Finally, conclusions and directions of future works are included
in section \ref{sec:conclusions}.

@@

\begin{description}
  \item[Consistency.]
       All objects (basic or composed) share a consistent interface composed of
       a limited set of methods. This interface is documented in a consistent
       manner for all objects.
  \item[Inspection.]
       Constructor parameters and parameter values determined by learning
       algorithms are stored and exposed as public attributes.
  \item[Non-proliferation of classes.]
       Learning algorithms are the only objects to be of custom classes.
       Datasets and hyperparameter names and values are represented as standard
       Python, NumPy or SciPy classes rather than new ones whenever feasible.
       This keeps \sklearn easy to use and easy to combine with other libraries.
       % XXX do we need to elaborate more on this, or do we expect everyone
       % to be an experienced Java/adapter pattern hater?
  % Gilles: this is actually not a design principle
  \item[Composition.]
       Many machine learning tasks are expressible
       as sequences or combinations of transformations to data.
       Some learning algorithms are also naturally viewed
       as meta-algorithms parameterized on other algorithms.
       Whenever possible, those algorithms are composed from
       existing building blocks.
       % Gilles: let elaborate later on the syntax
       % and a simple syntax is implemented
       % for setting and retrieving parameters of sub-estimators.
       % XXX need to describe this!
  \item[Sensible defaults.]
       Whenever an operation requires a user-defined parameter,
       a default and appropriate value is defined by the library.
       The default value should cause the operation to be performed
       in a sensible way (giving a baseline solution for the task at hand).
\end{description}

>>>>

In a previous paper \citep{pedregosa2011}, \sklearn was briefly presented and
benchmarked against several competitors. In this paper, we instead focus on an
in-depth discussion and analysis of the design choices used in building the
library. First, in section \ref{sec:core-api}, we present the central application
programming interface (API) and then describe, in section \ref{sec:advanced-api},
advanced API mechanisms built from the core interface. Section
\ref{sec:implementation} describes implementation trade-offs and analyzes
limitations of the technologies we rely on, while section
\ref{sec:comparison} then compares \emph{scikit-learn} to other major projects in
terms of API. Finally, conclusions and directions of future works are included
in section \ref{sec:conclusions}.

@@

\begin{description}
  \item[Consistency.]
       All objects (basic or composed) share a consistent interface composed of
       a limited set of methods. This interface is documented in a consistent
       manner for all objects.
  \item[Inspection.]
       Constructor parameters and parameter values determined by learning
       algorithms are stored and exposed as public attributes.
  \item[Non-proliferation of classes.]
       Learning algorithms are the only objects to be of custom classes.
       Datasets and hyperparameter names and values are represented as standard
       Python, NumPy or SciPy classes rather than new ones whenever feasible.
       This keeps \sklearn easy to use and easy to combine with other libraries.
       % XXX do we need to elaborate more on this, or do we expect everyone
       % to be an experienced Java/adapter pattern hater?
  \item[Composition.]
       Many machine learning tasks are expressible
       as sequences or combinations of transformations to data.
       Some learning algorithms are also naturally viewed
       as meta-algorithms parameterized on other algorithms.
       Whenever possible, those algorithms are implemented and composed from
       existing building blocks.
  \item[Sensible defaults.]
       Whenever an operation requires a user-defined parameter,
       a default and appropriate value is defined by the library.
       The default value should cause the operation to be performed
       in a sensible way (giving a baseline solution for the task at hand).
\end{description}
